Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-07-02 article.tex
p-value and pr-value for 500 agents and selection percent correction

This function ensures that each good has the same weight in the final score, i.e. managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent.
%\begin{figure}[htp]
%	\begin{center}
%		\includegraphics[width=7cm]{img/fitness.pdf}
%	\end{center}
%	\caption{The payoff depending on the quantity owned of a given good and the effective needs $n(g)$ for this good.}
%	\label{fig:fit}
%\end{figure}
%Figure~\ref{fig:fit} depicts the score of an agent, for different need values of one good, with regards to the quantity of the good possessed by the agent. We can see that even if the need for a good is small (for instance when $n(g) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need. This ensures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.
The complete score of an agent $i$ is termed $s^i$ and corresponds to the sum of the $s^i_j$. An agent will choose from whom the price vector should be copied among the agents that produce the same good and have the highest score. In practice, the worst two percent of the agents (in terms of score) will copy the prices of the best two percent. This selection process is detailed in algorithm~\ref{algo:selectionCulture}.

\begin{algorithm}
\caption{Selection Process}
\label{algo:selectionCulture}
	\begin{algorithmic}[1]
	\scriptsize
	\State	$ToGet = 0.2 \times \#Pop$
	\For{$g \in Good$}
		\State	$ToReplace = \{\}$
                \While{$\#ToReplace < ToGet$} 
			\State $ j = SelectRand(Pop,g) $ \Comment{Select randomly an agent $j$ among the agents producing $g$}
			\State $X \sim U([0,1])$ \Comment{Draw a random number from the uniform distribution between 0 and 1}
			\If{$X>ComputeScore(j)$} \Comment{Select preferably the agents with the lowest scores}
				\State $ToReplace = \{ToReplace,j\}$
			\EndIf
		\EndWhile

@@

\todo{complete table with final result (here it's just false exemple)}
\begin{table}[!h]
	\centering
	\begin{tabular}{cc|ccc}
		\multicolumn{2}{r}{}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
			N&$\mu$ & $\alpha$ ($sd$) & $p$-value ($sd$ - $pr$) &$\alpha$ ($sd$)\\\hline
		250	&0.004&1.53 (0.03)&0.58 (0.24 - .01)&1.54 (0.02)\\
			&0.016&1.57 (0.02)&0.35 (0.26 - .05)&1.57 (0.01)\\
			&0.064&1.66 (0.01)&0.0 (0.00 - 1)&1.67 (0.01)\\\hline
		500	&0.004&1.50 (0.02)&0.6 (0.05)&1.53 (0.03)\\
			&0.016&1.55 (0.03)&0.3 (0.05)&1.61 (0.04)\\
			&0.064&1.78 (0.08)&0.0 (0.00)&1.81 (0.10)\\
	\end{tabular}
	\caption{Mean $\alpha$ \& $sd$ are calculated on 100 runs for our results, and 5 runs for Bentley et. al. 2004. $pr$ is the percentage of run for which the $p$-value is less than 0.05, i.e. the percentage of runs for which we rejected the null-hypotheses stating that the distribution follow a power law.}
	\label{tab:mualpha}
\end{table}

@@

	\end{center}
	\caption{Proportions distribution, where each points represent the mean for 100 runs, for: a) the neutral and the trading models.  b) the neutral model and the trading model without the trading innovation process. c) the trade model and the trade model without the trading innovation process.}
	\label{fig:2setDi}
\end{figure}

On figure~\ref{fig:2setDi}.a) it appears that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis. In more details, the proportion distribution has a plateau of common prices (a number of prices share similar and high proportions), which shows that, when trade is taken into account, the most common variants are more diverse.

>>>>

This function ensures that each good has the same weight in the final score, i.e. managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent.
%\begin{figure}[htp]
%	\begin{center}
%		\includegraphics[width=7cm]{img/fitness.pdf}
%	\end{center}
%	\caption{The payoff depending on the quantity owned of a given good and the effective needs $n(g)$ for this good.}
%	\label{fig:fit}
%\end{figure}
%Figure~\ref{fig:fit} depicts the score of an agent, for different need values of one good, with regards to the quantity of the good possessed by the agent. We can see that even if the need for a good is small (for instance when $n(g) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need. This ensures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.
The complete score of an agent $i$ is termed $s^i$ and corresponds to the sum of the $s^i_j$. An agent will choose from whom the price vector should be copied among the agents that produce the same good and have the highest score. In practice, the worst (in terms of score) 20 percent of the agents producing the same good will copy the prices of the best twenty percent producing the same good. This selection process is detailed in algorithm~\ref{algo:selectionCulture}.

\begin{algorithm}
\caption{Selection Process}
\label{algo:selectionCulture}
	\begin{algorithmic}[1]
	\scriptsize
	\State	$ToGet = 0.2 \times \frac{\#Pop}{\#Good}$
	\For{$g \in Good$}
		\State	$ToReplace = \{\}$
                \While{$\#ToReplace < ToGet$} 
			\State $ j = SelectRand(Pop,g) $ \Comment{Select randomly an agent $j$ among the agents producing $g$}
			\State $X \sim U([0,1])$ \Comment{Draw a random number from the uniform distribution between 0 and 1}
			\If{$X>ComputeScore(j)$} \Comment{Select preferably the agents with the lowest scores}
				\State $ToReplace = \{ToReplace,j\}$
			\EndIf
		\EndWhile

@@

\todo{complete table with final result (here it's just false exemple)}
\begin{table}[!h]
	\centering
	\begin{tabular}{cc|ccc}
		\multicolumn{2}{r}{}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
			N&$\mu$ & $\alpha$ ($sd$) & $p$-value ($sd$ - $pr$) &$\alpha$ ($sd$)\\\hline
		250	&0.004&1.53 (0.03)&0.58 (0.24 - .01)&1.54 (0.02)\\
			&0.016&1.57 (0.02)&0.35 (0.28 - .05)&1.57 (0.01)\\
			&0.064&1.66 (0.01)&0.0 (0.00 - 1)&1.67 (0.01)\\\hline
		500	&0.004&1.50 (0.02)&0.59 (0.28 - .02 )&1.53 (0.03)\\
			&0.016&1.55 (0.03)&0.15 (0.17 - .10 )&1.61 (0.04)\\
			&0.064&1.78 (0.08)&0.0 (0.00 - 1)&1.81 (0.10)\\
	\end{tabular}
	\caption{Mean $\alpha$ \& $sd$ are calculated on 100 runs for our results, and 5 runs for Bentley et. al. 2004. $pr$ is the percentage of run for which the $p$-value is less than 0.05, i.e. the percentage of runs for which we rejected the null-hypotheses stating that the distribution follow a power law.}
	\label{tab:mualpha}
\end{table}

@@

	\end{center}
	\caption{Frequencies distribution, where each points represent the mean for 100 runs, for: a) the neutral and the trading models.  b) the neutral model and the trading model without the trading innovation process. c) the trade model and the trade model without the trading innovation process.}
	\label{fig:2setDi}
\end{figure}

On figure~\ref{fig:2setDi}.a) it appears that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis. In more details, the frequencies distribution has a plateau of common prices (a number of prices share similar and high proportions), which shows that, when trade is taken into account, the most common variants are more diverse.
